---
title: "Simulation results predictive performance simulation study II"
authors: "Ginette Lafit"
date: 23-02-2021
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initial set up


```{r definition, echo = TRUE}
ls()

rm(list=ls())

library(ggplot2)
library(gridExtra)
library(sjstats)
library(dplyr)
library(knitr)
library(rstatix)
library(lme4)

######################################################################################
######################################################################################
######################################################################################

# Upload the functions
source(file="Performance.PC.VAR.MSPE.Anova.Q1.R")
source(file="Performance.PC.VAR.MSPE.Anova.Q23.R")

######################################################################################
######################################################################################
######################################################################################

# Set the values to simulate data assuming a VAR(1) process
set.seed(123) # Set random seed
N = 60 # Number of participants
T = c(50,100) # Number of time points
P = c(2,4,8) # Number of variables in VAR(1) models
Effect = c(1,2) # Effects fixed (1) or random (2)
N = 60 # Number of participants
P = 6 # Number of variables 
Q = c(1,2,3) # Number of components in VAR(1) models
E = c(1,2) # variance of the error to re-scale the expected noise variance of the observed variables: 1 is 5% and 2 is 50%

# Set the number of replicates
R = 100 # Number of replicates

```


## True number of components: 1 

### Repeated Measurement Anova

#### MSPE

```{r}
Model.names.Q1 = c('MAR.FE','MAR.RE','MVAR.FE','MVAR.RE','AR','VAR',
                       'PC.AR','PC.MAR.FE','PC.MAR.RE')

RM.Anova.MSPE.Q1 = Performance.PC.VAR.MSPE.Anova.Q1(N,T,P,Q=1,E,Effect,R)
save(RM.Anova.MSPE.Q1, file = 'Results_Performance_Study_II_Q1.RData')

load(file = 'Results_Performance_Study_II_Q1.RData')

# Change labels for error variance

RM.Anova.MSPE.Q1$Error = ifelse(RM.Anova.MSPE.Q1$Error == 1,5,50)

# Convert id and time into factor variables
RM.Anova.MSPE.Q1 <- RM.Anova.MSPE.Q1 %>%
  convert_as_factor(Time,Persons,Variables,Model,Error,Effect,Factors,id)

RM.Anova.MSPE.Q1$id.dat = as.numeric(interaction(RM.Anova.MSPE.Q1$Time,RM.Anova.MSPE.Q1$Variables,
                                    RM.Anova.MSPE.Q1$Persons,RM.Anova.MSPE.Q1$id,
                                    RM.Anova.MSPE.Q1$Error,RM.Anova.MSPE.Q1$Effect,
                                    RM.Anova.MSPE.Q1$Factors))
```

#### Fixed effects

```{r}
RM.Anova.MSPE.Q1.FE = RM.Anova.MSPE.Q1

# Performance MSPE
RM.Anova.MSPE.Q1.FE = RM.Anova.MSPE.Q1.FE[RM.Anova.MSPE.Q1.FE$Effect==1,]

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Error*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE.Q1.FE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.Q1.FE %>% 
  group_by(Model,Time,Error) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_PC_MVAR_FE_Q_1 = ggplot(RM.Anova.MSPE.Q1.FE, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_FE_Q_1

ggsave("Boxplot_MSPE_PC_MVAR_FE_Q_1.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
Performance.MSPE.Mean.Model.Q1 = RM.Anova.MSPE.Q1.FE

Performance.MSPE.Mean.Model.Q1 = Performance.MSPE.Mean.Model.Q1[Performance.MSPE.Mean.Model.Q1$Model==c('PC.MAR.FE','PC.MAR.RE'),]


Boxplot_MSPE_PC_MVAR_FE_Q_1_Models = ggplot(Performance.MSPE.Mean.Model.Q1, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_FE_Q_1_Models

ggsave("Boxplot_MSPE_PC_MVAR_FE_Q_1_Models.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q1.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q1.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```


#### Random effects

```{r}
RM.Anova.MSPE.Q1.RE = RM.Anova.MSPE.Q1

# Performance MSPE
RM.Anova.MSPE.Q1.RE = RM.Anova.MSPE.Q1.RE[RM.Anova.MSPE.Q1.RE$Effect==2,]

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Error*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE.Q1.RE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.Q1.RE %>% 
  group_by(Model,Time,Error) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_PC_MVAR_RE_Q_1 = ggplot(RM.Anova.MSPE.Q1.RE, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_1

ggsave("Boxplot_MSPE_PC_MVAR_RE_Q_1.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
Performance.MSPE.Mean.Model.Q1 = RM.Anova.MSPE.Q1.RE

Performance.MSPE.Mean.Model.Q1 = Performance.MSPE.Mean.Model.Q1[Performance.MSPE.Mean.Model.Q1$Model==c('PC.MAR.FE','PC.MAR.RE'),]


Boxplot_MSPE_PC_MVAR_RE_Q_1_Models = ggplot(Performance.MSPE.Mean.Model.Q1, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_1_Models

ggsave("Boxplot_MSPE_PC_MVAR_RE_Q_1_Models.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q1.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Model selection using the one standard error rule for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q1.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```

## True number of components: 2 

### Repeated Measurement Anova

#### MSPE

```{r}
Model.names.Q2 = c('MAR.FE','MAR.RE','MVAR.FE','MVAR.RE','AR','VAR',
                       'PC.VAR','PC.MAR.FE','PC.MAR.RE','PC.MVAR.FE','PC.MVAR.RE')

RM.Anova.MSPE.Q2 = Performance.PC.VAR.MSPE.Anova.Q23(N,T,P,Q=2,E,Effect,R)
save(RM.Anova.MSPE.Q2, file = 'Results_Performance_Study_II_Q2.RData')

load(file = 'Results_Performance_Study_II_Q2.RData')

# Change labels for error variance

RM.Anova.MSPE.Q2$Error = ifelse(RM.Anova.MSPE.Q2$Error == 1,5,50)

# Convert id and time into factor variables
RM.Anova.MSPE.Q2 <- RM.Anova.MSPE.Q2 %>%
  convert_as_factor(Time,Persons,Variables,Model,Error,Effect,Factors,id)

RM.Anova.MSPE.Q2$id.dat = as.numeric(interaction(RM.Anova.MSPE.Q2$Time,RM.Anova.MSPE.Q2$Variables,
                                    RM.Anova.MSPE.Q2$Persons,RM.Anova.MSPE.Q2$id,
                                    RM.Anova.MSPE.Q2$Error,RM.Anova.MSPE.Q2$Effect,
                                    RM.Anova.MSPE.Q2$Factors))
```


#### Fixed effects

```{r}
RM.Anova.MSPE.Q2.FE = RM.Anova.MSPE.Q2

# Performance MSPE
RM.Anova.MSPE.Q2.FE = RM.Anova.MSPE.Q2.FE[RM.Anova.MSPE.Q2.FE$Effect==1,]

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Error*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE.Q2.FE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.Q2.FE %>% 
  group_by(Model,Time,Error) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_PC_MVAR_FE_Q_2 = ggplot(RM.Anova.MSPE.Q2.FE, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_FE_Q_2

ggsave("Boxplot_MSPE_PC_MVAR_FE_Q_2.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
Performance.MSPE.Mean.Model.Q2 = RM.Anova.MSPE.Q2.FE

Performance.MSPE.Mean.Model.Q2 = Performance.MSPE.Mean.Model.Q2[Performance.MSPE.Mean.Model.Q2$Model==c('PC.MVAR.FE','PC.MVAR.RE'),]


Boxplot_MSPE_PC_MVAR_RE_Q_2_Models = ggplot(Performance.MSPE.Mean.Model.Q2, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_2_Models

ggsave("Boxplot_MSPE_PC_MVAR_FE_Models_Q_2.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q2.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Model selection using the one standard error rule for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q2.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```


#### Random effects

```{r}
RM.Anova.MSPE.Q2.RE = RM.Anova.MSPE.Q2

# Performance MSPE
RM.Anova.MSPE.Q2.RE = RM.Anova.MSPE.Q2.RE[RM.Anova.MSPE.Q2.RE$Effect==2,]

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Error*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE.Q2.FE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.Q2.RE %>% 
  group_by(Model,Time,Error) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_PC_MVAR_RE_Q_2 = ggplot(RM.Anova.MSPE.Q2.RE, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_2

ggsave("Boxplot_MSPE_PC_MVAR_RE_Q_2.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
Performance.MSPE.Mean.Model.Q2 = RM.Anova.MSPE.Q2.RE

Performance.MSPE.Mean.Model.Q2 = Performance.MSPE.Mean.Model.Q2[Performance.MSPE.Mean.Model.Q2$Model==c('PC.MVAR.FE','PC.MVAR.RE'),]


Boxplot_MSPE_PC_MVAR_RE_Q_2_Models = ggplot(Performance.MSPE.Mean.Model.Q2, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_2_Models

ggsave("Boxplot_MSPE_PC_MVAR_RE_Models_Q_2.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q2.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Model selection using the one standard error rule for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q2.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```


## True number of components: 3 

### Repeated Measurement Anova

#### MSPE

```{r}
Model.names.Q3 = c('MAR.FE','MAR.RE','MVAR.FE','MVAR.RE','AR','VAR',
                       'PC.VAR','PC.MAR.FE','PC.MAR.RE','PC.MVAR.FE','PC.MVAR.RE')

RM.Anova.MSPE.Q3 = Performance.PC.VAR.MSPE.Anova.Q23(N,T,P,Q=3,E,Effect,R)
save(RM.Anova.MSPE.Q3, file = 'Results_Performance_Study_II_Q3.RData')

load(file = 'Results_Performance_Study_II_Q3.RData')

# Change labels for error variance

RM.Anova.MSPE.Q3$Error = ifelse(RM.Anova.MSPE.Q3$Error == 1,5,50)

# Convert id and time into factor variables
RM.Anova.MSPE.Q3 <- RM.Anova.MSPE.Q3 %>%
  convert_as_factor(Time,Persons,Variables,Model,Error,Effect,Factors,id)

RM.Anova.MSPE.Q3$id.dat = as.numeric(interaction(RM.Anova.MSPE.Q3$Time,RM.Anova.MSPE.Q3$Variables,
                                    RM.Anova.MSPE.Q3$Persons,RM.Anova.MSPE.Q3$id,
                                    RM.Anova.MSPE.Q3$Error,RM.Anova.MSPE.Q3$Effect,
                                    RM.Anova.MSPE.Q3$Factors))
```


#### Fixed effects

```{r}
RM.Anova.MSPE.Q3.FE = RM.Anova.MSPE.Q3

# Performance MSPE
RM.Anova.MSPE.Q3.FE = RM.Anova.MSPE.Q3.FE[RM.Anova.MSPE.Q3.FE$Effect==1,]

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Error*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE.Q3.FE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.Q3.FE %>% 
  group_by(Model,Time,Error) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_PC_MVAR_FE_Q_3 = ggplot(RM.Anova.MSPE.Q3.FE, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_FE_Q_3

ggsave("Boxplot_MSPE_PC_MVAR_FE_Q_3.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
Performance.MSPE.Mean.Model.Q3 = RM.Anova.MSPE.Q3.FE

Performance.MSPE.Mean.Model.Q3 = Performance.MSPE.Mean.Model.Q3[Performance.MSPE.Mean.Model.Q3$Model==c('PC.MVAR.FE','PC.MVAR.RE'),]


Boxplot_MSPE_PC_MVAR_RE_Q_3_Models = ggplot(Performance.MSPE.Mean.Model.Q3, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_3_Models

ggsave("Boxplot_MSPE_PC_MVAR_FE_Models_Q_3.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q3.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Model selection using the one standard error rule for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q3.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```


#### Random effects

```{r}
RM.Anova.MSPE.Q3.RE = RM.Anova.MSPE.Q3

# Performance MSPE
RM.Anova.MSPE.Q3.RE = RM.Anova.MSPE.Q3.RE[RM.Anova.MSPE.Q3.RE$Effect==2,]

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Error*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE.Q3.FE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.Q3.RE %>% 
  group_by(Model,Time,Error) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_PC_MVAR_RE_Q_3 = ggplot(RM.Anova.MSPE.Q3.RE, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_3

ggsave("Boxplot_MSPE_PC_MVAR_RE_Q_3.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
Performance.MSPE.Mean.Model.Q3 = RM.Anova.MSPE.Q3.RE

Performance.MSPE.Mean.Model.Q3 = Performance.MSPE.Mean.Model.Q3[Performance.MSPE.Mean.Model.Q3$Model==c('PC.MVAR.FE','PC.MVAR.RE'),]


Boxplot_MSPE_PC_MVAR_RE_Q_3_Models = ggplot(Performance.MSPE.Mean.Model.Q3, aes(x=interaction(Time,Error), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and noise variance")
Boxplot_MSPE_PC_MVAR_RE_Q_3_Models

ggsave("Boxplot_MSPE_PC_MVAR_RE_Models_Q_3.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q3.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Model selection using the one standard error rule for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.Q3.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```

