---
title: "Simulation results predictive performance simulation study III"
authors: "Ginette Lafit"
date: 23-02-2021
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initial set up


```{r definition, echo = TRUE}
ls()

rm(list=ls())

library(ggplot2)
library(gridExtra)
library(sjstats)
library(dplyr)
library(knitr)
library(rstatix)
library(lme4)

######################################################################################
######################################################################################
######################################################################################

# Upload the functions
source(file="Performance.Cluster.VAR.MSPE.Anova.R")

######################################################################################
######################################################################################
######################################################################################

Effect = c(1,2) # Type of effects (1=fixed) and (2=random)
N = c(20,60) # Number of participants
T = c(50,100,200) # Number of time points
P = 4 # Number of variables in VAR(1) models
K = c(2,4) # Number of clusters
D = 1 # Difference between clusters
S = c(1,2,3) # Distributions of persons across clusters

# Set the number of replicates
R = 100 # Number of replicates

```


## Fixed Effects 

### Repeated Measurement Anova

#### MSPE

```{r}
#RM.Anova.MSPE.FE = Performance.Cluster.VAR.MSPE.Anova(N,T,P,K,S,D,Effect=1,R)
#save(RM.Anova.MSPE.FE, file = 'Results_Performance_Study_III_FE.RData')

load(file = 'Results_Performance_Study_III_FE.RData')

# Convert id and time into factor variables
RM.Anova.MSPE.FE <- RM.Anova.MSPE.FE %>%
  convert_as_factor(Time,Persons,Variables,Model,Clusters,Size,Diff,Effect,id)

RM.Anova.MSPE.FE$id.dat = as.numeric(interaction(RM.Anova.MSPE.FE$Time,RM.Anova.MSPE.FE$Variables,
                                    RM.Anova.MSPE.FE$Persons,RM.Anova.MSPE.FE$id,
                                    RM.Anova.MSPE.FE$Clusters,RM.Anova.MSPE.FE$Effect,
                                    RM.Anova.MSPE.FE$Diff,
                                    RM.Anova.MSPE.FE$Size))
```

#### Anova

```{r}
# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Persons*Clusters*Model*Size + Error(id.dat/Model),
  data = RM.Anova.MSPE.FE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.FE %>% 
  group_by(Model,Size,Clusters,Persons,Time) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_Cluster_MVAR_FE = ggplot(RM.Anova.MSPE.FE, aes(x=interaction(Time,Clusters), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and number of clusters")
Boxplot_MSPE_Cluster_MVAR_FE

ggsave("Boxplot_MSPE_Cluster_MVAR_FE.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
RM.Anova.MSPE.FE.Model = RM.Anova.MSPE.FE

RM.Anova.MSPE.FE.Model = RM.Anova.MSPE.FE.Model[RM.Anova.MSPE.FE.Model$Model==c('MVAR.FE','MVAR.RE'),]


Boxplot_MSPE_Cluster_MVAR_FE_Models = ggplot(RM.Anova.MSPE.FE.Model, aes(x=interaction(Time,Clusters), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and number of clusters")
Boxplot_MSPE_Cluster_MVAR_FE_Models

ggsave("Boxplot_MSPE_Cluster_MVAR_FE_Models.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Method with the minimum MSE using the one standard error rule

```{r}
colMeans(table(RM.Anova.MSPE.FE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```


## Random Effects 

### Repeated Measurement Anova

#### MSPE

```{r}
#RM.Anova.MSPE.RE = Performance.Cluster.VAR.MSPE.Anova(N,T,P,K,S,D,Effect=2,R)
#save(RM.Anova.MSPE.RE, file = 'Results_Performance_Study_III_RE.RData')

load(file = 'Results_Performance_Study_III_RE.RData')

# Convert id and time into factor variables
RM.Anova.MSPE.RE <- RM.Anova.MSPE.RE %>%
  convert_as_factor(Time,Persons,Variables,Model,Clusters,Size,Diff,Effect,id)

RM.Anova.MSPE.RE$id.dat = as.numeric(interaction(RM.Anova.MSPE.RE$Time,RM.Anova.MSPE.RE$Variables,
                                    RM.Anova.MSPE.RE$Persons,RM.Anova.MSPE.RE$id,
                                    RM.Anova.MSPE.RE$Clusters,RM.Anova.MSPE.RE$Effect,
                                    RM.Anova.MSPE.RE$Diff,
                                    RM.Anova.MSPE.RE$Size))
```

#### Anova

```{r}
# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Persons*Clusters*Model*Size + Error(id.dat/Model),
  data = RM.Anova.MSPE.RE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

##### Mean and standard deviation

###### Across the number of time points

```{r}
kable(RM.Anova.MSPE.RE %>% 
  group_by(Model,Size,Clusters,Persons,Time) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 4)
```

##### Boxplots

###### Across the number of time points

```{r}
Boxplot_MSPE_Cluster_MVAR_RE = ggplot(RM.Anova.MSPE.RE, aes(x=interaction(Time,Clusters), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and number of clusters")
Boxplot_MSPE_Cluster_MVAR_RE

ggsave("Boxplot_MSPE_Cluster_MVAR_RE.png", width = 6, height = 4)

```

###### Across the number of time points selected models

```{r}
RM.Anova.MSPE.RE.Model = RM.Anova.MSPE.RE

RM.Anova.MSPE.RE.Model = RM.Anova.MSPE.RE.Model[RM.Anova.MSPE.RE.Model$Model==c('VAR','MVAR.RE'),]


Boxplot_MSPE_Cluster_MVAR_RE_Models = ggplot(RM.Anova.MSPE.RE.Model, aes(x=interaction(Time,Clusters), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + 
theme(axis.text.x = element_text(angle = 90)) +
labs(y = "MSPE", x="Number of time points and number of clusters")
Boxplot_MSPE_Cluster_MVAR_RE_Models

ggsave("Boxplot_MSPE_Cluster_MVAR_RE_Models.png", width = 6, height = 4)

```


###### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(RM.Anova.MSPE.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

###### Method with the minimum MSE using the one standard error rule

```{r}
colMeans(table(RM.Anova.MSPE.RE %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```
