---
title: "Simulation results predictive performance multilevel VAR(1) model with fixed effects"
authors: "Ginette Lafit"
date: 23-02-2021
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initial set up


```{r definition, echo = TRUE}
ls()

rm(list=ls())

library(ggplot2)
library(gridExtra)
library(sjstats)
library(dplyr)
library(knitr)
library(rstatix)
library(lme4)

######################################################################################
######################################################################################
######################################################################################

# Upload the functions
source(file="Performance.VAR.MSPE.Anova.R")
source(file="Performance.VAR.R2.Anova.R")

######################################################################################
######################################################################################
######################################################################################

# Set the values to simulate data assuming a VAR(1) process
set.seed(123) # Set random seed
N = c(20,60,120) # Number of participants
T = c(50,100,200) # Number of time points
P = c(2,4,8) # Number of variables in VAR(1) models

Model.names = c('MAR.FE','MAR.RE','MVAR.FE','MVAR.RE','AR','VAR')

# Set the number of replicates
R = 100 # Number of replicates
```


### Repeated Measurement Anova

#### MSPE

```{r}
#RM.Anova.MSPE = Performance.VAR.MSPE.Anova(N,T,P,R)
#save(RM.Anova.MSPE, file = 'Results_Performance_MSPE_MVAR_FE.RData')

load(file = 'Results_Performance_MSPE_MVAR_FE.RData')

# Convert id and time into factor variables
RM.Anova.MSPE <- RM.Anova.MSPE %>%
  convert_as_factor(Time,Persons,Variables,Model,id)

RM.Anova.MSPE$id.dat = as.numeric(interaction(RM.Anova.MSPE$Time,RM.Anova.MSPE$Variables,
                                    RM.Anova.MSPE$Persons,RM.Anova.MSPE$id))

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Persons*Variables*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

# Compute main effects

Model.effect <- RM.Anova.MSPE %>%
  group_by(Model) %>%
  anova_test(dv = MSPE, wid = id.dat, between = c(Time,Persons,Variables))
Model.effect

# Fit pairwise comparisons
pwc <- RM.Anova.MSPE %>%
  group_by(Time, Persons, Variables) %>%
  pairwise_t_test(MSPE ~ Model, p.adjust.method = "bonferroni") %>%
  select(-p, -p.signif) # Remove details
pwc
```

#### R2

```{r}
#RM.Anova.R2 = Performance.VAR.R2.Anova(N,T,P,R)
#save(RM.Anova.R2, file = 'Results_Performance_R2_MVAR_FE.RData')

load(file = 'Results_Performance_R2_MVAR_FE.RData')

# Convert id and time into factor variables
RM.Anova.R2 <- RM.Anova.R2 %>%
  convert_as_factor(Time,Persons,Variables,Model,id)

RM.Anova.R2$id.dat = as.numeric(interaction(RM.Anova.R2$Time,RM.Anova.R2$Variables,
                                    RM.Anova.R2$Persons,RM.Anova.R2$id))

# Mixed ANOVA 

fit.R2 = aov(
  R2 ~ Time*Persons*Variables*Model + Error(id.dat/Model),
  data = RM.Anova.R2
)

# Summary repeated measurement Anova
summary.anova.R2 = summary(fit.R2)
summary.anova.R2

# Eta squared
eta.R2 = effectsize::eta_squared(fit.R2,ci = 0.95)
eta.R2

# Compute main effects

Model.effect <- RM.Anova.R2 %>%
  group_by(Model) %>%
  anova_test(dv = R2, wid = id.dat, between = c(Time,Persons,Variables))
Model.effect

# Fit pairwise comparisons
pwc <- RM.Anova.R2 %>%
  group_by(Time, Persons, Variables) %>%
  pairwise_t_test(R2 ~ Model, p.adjust.method = "bonferroni") %>%
  select(-p, -p.signif) # Remove details
pwc
```


### Boxplot interaction effects

```{r}
# Performance MSPE for MVAR and VAR
Performance.MSPE.Mean.Model = RM.Anova.MSPE

Performance.MSPE.Mean.Model = Performance.MSPE.Mean.Model[Performance.MSPE.Mean.Model$Model==c('MVAR.FE','MVAR.RE'),]

Boxplot_MSPE_MVAR_FE_Time_Variables = ggplot(Performance.MSPE.Mean.Model, aes(x=interaction(Time,Variables), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_brewer(palette = "Set1") + theme_bw() + facet_grid(~Model) +
labs(x="Number of time points and variables") + theme(axis.text.x = element_text(angle = 90))
Boxplot_MSPE_MVAR_FE_Time_Variables

ggsave("Boxplot_MSPE_MVAR_FE_Time_Variables.png", width = 6, height = 4)
```


### $P=2$

#### Performance measure: MSPE 

```{r}
Performance.MSPE.Mean.P2 = RM.Anova.MSPE

# Performance MSPE
Performance.MSPE.Mean.P2 = Performance.MSPE.Mean.P2[Performance.MSPE.Mean.P2$Variables==2,]
```

#### Mean and standard deviation

##### Across the number of time points

```{r}
kable(Performance.MSPE.Mean.P2 %>% 
  group_by(Model,Time) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.MSPE.Mean.P2 %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

#### Boxplots

##### Across the number of time points

```{r}
Boxplot_MSPE_MVAR_FE_P_2_Time = ggplot(Performance.MSPE.Mean.P2, aes(x=as.factor(Time), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSPE", x="Number of time points")
Boxplot_MSPE_MVAR_FE_P_2_Time

ggsave("Boxplot_MSPE_MVAR_FE_P_2_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_MSPE_MVAR_FE_P_2_Persons = ggplot(Performance.MSPE.Mean.P2, aes(x=as.factor(Persons), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "MSPE", x="Number of persons")
Boxplot_MSPE_MVAR_FE_P_2_Persons

ggsave("Boxplot_MSPE_MVAR_FE_P_2_Persons.png", width = 6, height = 4)

```


#### Performance measure: $R^2$

```{r}
Performance.R2.Mean.P2 = RM.Anova.R2

# Performance MSPE
Performance.R2.Mean.P2 = Performance.R2.Mean.P2[Performance.R2.Mean.P2$Variables==2,]
```

#### Mean and standard deviation

##### Across the number of time points

```{r}
kable(Performance.R2.Mean.P2 %>% 
  group_by(Model,Time) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.R2.Mean.P2 %>% 
  group_by(Model,Persons) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

#### Boxplots

##### Across the number of time points

```{r}
Boxplot_R2_MVAR_FE_P_2_Time = ggplot(Performance.R2.Mean.P2, aes(x=as.factor(Time), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "R2", x="Number of time points")
Boxplot_R2_MVAR_FE_P_2_Time

ggsave("Boxplot_R2_MVAR_FE_P_2_Time.png", width = 6, height = 4)
```

##### Across the number of persons

```{r}
Boxplot_R2_MVAR_FE_P_2_Persons = ggplot(Performance.R2.Mean.P2, aes(x=as.factor(Persons), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "R2", x="Number of persons")
Boxplot_R2_MVAR_FE_P_2_Persons

ggsave("Boxplot_R2_MVAR_FE_P_2_Persons.png", width = 6, height = 4)
```


### $P=4$

#### Performance measure: MSPE 

```{r}
Performance.MSPE.Mean.P4 = RM.Anova.MSPE

# Performance MSPE
Performance.MSPE.Mean.P4 = Performance.MSPE.Mean.P4[Performance.MSPE.Mean.P4$Variables==4,]
```

#### Mean and standard deviation

##### Across the number of time points

```{r}
kable(Performance.MSPE.Mean.P4 %>% 
  group_by(Model,Time) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.MSPE.Mean.P4 %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

#### Boxplots

##### Across the number of time points

```{r}
Boxplot_MSPE_MVAR_FE_P_4_Time = ggplot(Performance.MSPE.Mean.P4, aes(x=as.factor(Time), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSPE", x="Number of time points")
Boxplot_MSPE_MVAR_FE_P_4_Time

ggsave("Boxplot_MSPE_MVAR_FE_P_4_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_MSPE_MVAR_FE_P_4_Persons = ggplot(Performance.MSPE.Mean.P4, aes(x=as.factor(Persons), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "MSPE", x="Number of persons")
Boxplot_MSPE_MVAR_FE_P_4_Persons

```


#### Performance measure: $R^2$

```{r}
Performance.R2.Mean.P4 = RM.Anova.R2

# Performance MSPE
Performance.R2.Mean.P4 = Performance.R2.Mean.P4[Performance.R2.Mean.P4$Variables==4,]
```

#### Mean and standard deviation

##### Across the number of time points

```{r}
kable(Performance.R2.Mean.P4 %>% 
  group_by(Model,Time) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.R2.Mean.P4 %>% 
  group_by(Model,Persons) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

#### Boxplots

##### Across the number of time points

```{r}
Boxplot_R2_MVAR_FE_P_4_Time = ggplot(Performance.R2.Mean.P2, aes(x=as.factor(Time), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "R2", x="Number of time points")
Boxplot_R2_MVAR_FE_P_4_Time

ggsave("Boxplot_R2_MVAR_FE_P_4_Time.png", width = 6, height = 4)
```

##### Across the number of persons

```{r}
Boxplot_R2_MVAR_FE_P_4_Persons = ggplot(Performance.R2.Mean.P4, aes(x=as.factor(Persons), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "R2", x="Number of persons")
Boxplot_R2_MVAR_FE_P_4_Persons

ggsave("Boxplot_R2_MVAR_FE_P_4_Persons.png", width = 6, height = 4)
```


### $P=8$

#### Performance measure: MSPE 

```{r}
Performance.MSPE.Mean.P8 = RM.Anova.MSPE

# Performance MSPE
Performance.MSPE.Mean.P8 = Performance.MSPE.Mean.P8[Performance.MSPE.Mean.P8$Variables==8,]
```

#### Mean and standard deviation

##### Across the number of time points

```{r}
kable(Performance.MSPE.Mean.P8 %>% 
  group_by(Model,Time) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.MSPE.Mean.P8 %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

#### Boxplots

##### Across the number of time points

```{r}
Boxplot_MSPE_MVAR_FE_P_8_Time = ggplot(Performance.MSPE.Mean.P8, aes(x=as.factor(Time), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSPE", x="Number of time points")
Boxplot_MSPE_MVAR_FE_P_8_Time

ggsave("Boxplot_MSPE_MVAR_FE_P_8_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_MSPE_MVAR_FE_P_8_Persons = ggplot(Performance.MSPE.Mean.P8, aes(x=as.factor(Persons), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "MSPE", x="Number of persons")
Boxplot_MSPE_MVAR_FE_P_8_Persons

ggsave("Boxplot_MSPE_MVAR_FE_P_8_Persons.png", width = 6, height = 4)

```


#### Performance measure: $R^2$

```{r}
Performance.R2.Mean.P8 = RM.Anova.R2

# Performance MSPE
Performance.R2.Mean.P8 = Performance.R2.Mean.P8[Performance.R2.Mean.P8$Variables==8,]
```

#### Mean and standard deviation

##### Across the number of time points

```{r}
kable(Performance.R2.Mean.P8 %>% 
  group_by(Model,Time) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.R2.Mean.P8 %>% 
  group_by(Model,Persons) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

#### Boxplots

##### Across the number of time points

```{r}
Boxplot_R2_MVAR_FE_P_8_Time = ggplot(Performance.R2.Mean.P8, aes(x=as.factor(Time), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "R2", x="Number of time points")
Boxplot_R2_MVAR_FE_P_8_Time

ggsave("Boxplot_R2_MVAR_FE_P_8_Time.png", width = 6, height = 4)
```

##### Across the number of persons

```{r}
Boxplot_R2_MVAR_FE_P_8_Persons = ggplot(Performance.R2.Mean.P8, aes(x=as.factor(Persons), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "R2", x="Number of persons")
Boxplot_R2_MVAR_FE_P_8_Persons

ggsave("Boxplot_R2_MVAR_FE_P_8_Persons.png", width = 6, height = 4)
```


### Performance measures: MSPE

#### Data set


```{r}
Performance.MSPE.Mean = RM.Anova.MSPE
```


#### Mean and standard deviation

##### Across the number of variables

```{r}
kable(Performance.MSPE.Mean %>% 
  group_by(Model,Variables) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

##### Across the number of time points

```{r}
kable(Performance.MSPE.Mean %>% 
  group_by(Model,Time) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.MSPE.Mean %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

#### Boxplots

##### Across the number of variables

```{r}
Boxplot_MSPE_MVAR_FE_Variables = ggplot(Performance.MSPE.Mean, aes(x=as.factor(Variables), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw()+ 
labs(y = "MSPE", x="Number of variables")
Boxplot_MSPE_MVAR_FE_Variables

ggsave("Boxplot_MSPE_MVAR_FE_Variables.png", width = 6, height = 4)

``` 

##### Across the number of time points

```{r}
Boxplot_MSPE_MVAR_FE_Time = ggplot(Performance.MSPE.Mean, aes(x=as.factor(Time), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSPE",x="Number of time points")
Boxplot_MSPE_MVAR_FE_Time

ggsave("Boxplot_MSPE_MVAR_FE_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_MSPE_MVAR_FE_Persons = ggplot(Performance.MSPE.Mean, aes(x=as.factor(Persons), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "MSPE", x="Number of persons")
Boxplot_MSPE_MVAR_FE_Persons

ggsave("Boxplot_MSPE_MVAR_FE_Persons.png", width = 6, height = 4)

```

### Performance measures: R2

#### Data set


```{r}
Performance.R2.Mean = RM.Anova.R2
```


#### Mean and standard deviation

##### Across the number of variables

```{r}
kable(Performance.R2.Mean %>% 
  group_by(Model,Variables) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

##### Across the number of time points

```{r}
kable(Performance.R2.Mean %>% 
  group_by(Model,Time) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.R2.Mean %>% 
  group_by(Model,Persons) %>% 
  summarize(mean = mean(R2),
            sd = sd(R2)), digits = 3)
```

#### Boxplots

##### Across the number of variables

```{r}
Boxplot_R2_MVAR_FE_Variables = ggplot(Performance.R2.Mean, aes(x=as.factor(Variables), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(x="Number of variables")
Boxplot_R2_MVAR_FE_Variables

ggsave("Boxplot_R2_MVAR_FE_Variables.png", width = 6, height = 4)
```

##### Across the number of time points

```{r}
Boxplot_R2_MVAR_FE_Time = ggplot(Performance.R2.Mean, aes(x=as.factor(Time), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(x="Number of time points")
Boxplot_R2_MVAR_FE_Time

ggsave("Boxplot_R2_MVAR_FE_Time.png", width = 6, height = 4)
```

##### Across the number of persons

```{r}
Boxplot_R2_MVAR_FE_Persons = ggplot(Performance.R2.Mean, aes(x=as.factor(Persons), y=R2, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(x="Number of persons")
Boxplot_R2_MVAR_FE_Persons

ggsave("Boxplot_R2_MVAR_FE_Persons.png", width = 6, height = 4)
```

##### MEthod with the minimum MSE for each generated data set

```{r}
colMeans(table(Performance.MSPE.Mean %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

##### MEthod with the minimum MSE using the standard error rule for each generated data set

```{r}
colMeans(table(Performance.MSPE.Mean %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```

##### MEthod with the maximum R2 for each generated data set

```{r}
colMeans(table(Performance.R2.Mean %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.max(R2)])))
```

