---
title: "Simulation results predictive performance multilevel AR(1) model with random effects"
authors: "Ginette Lafit"
date: 23-02-2021
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initial set up


```{r definition, echo = TRUE}
ls()

rm(list=ls())

library(ggplot2)
library(gridExtra)
library(sjstats)
library(dplyr)
library(knitr)
library(rstatix)
library(lme4)

######################################################################################
######################################################################################
######################################################################################

# Upload the functions
source(file="Performance.VAR.MSPE.Anova.R")
source(file="Performance.VAR.R2.Anova.R")

######################################################################################
######################################################################################
######################################################################################

# Set the values to simulate data assuming a VAR(1) process
set.seed(123) # Set random seed
N = c(20,60,120) # Number of participants
T = c(50,100,200) # Number of time points
P = 4 # Number of variables in VAR(1) models

Model.names = c('MAR.FE','MAR.RE','MVAR.FE','MVAR.RE','AR','VAR')

# Set the number of replicates
R = 100 # Number of replicates
```


### Repeated Measurement Anova

#### MSPE

```{r}
#RM.Anova.MSPE = Performance.VAR.MSPE.Anova(N,T,P,R)
#save(RM.Anova.MSPE, file = 'Results_Performance_MSPE_MAR_RE.RData')

load(file = 'Results_Performance_MSPE_MAR_RE.RData')

# Convert id and time into factor variables
RM.Anova.MSPE <- RM.Anova.MSPE %>%
  convert_as_factor(Time,Persons,Variables,Model,id)

RM.Anova.MSPE$id.dat = as.numeric(interaction(RM.Anova.MSPE$Time,RM.Anova.MSPE$Variables,
                                    RM.Anova.MSPE$Persons,RM.Anova.MSPE$id))

# MSPE: Mixed ANOVA 

fit.MSPE = aov(
  MSPE ~ Time*Persons*Model + Error(id.dat/Model),
  data = RM.Anova.MSPE
)

# Summary repeated measurement Anova
summary.anova.MSPE = summary(fit.MSPE)
summary.anova.MSPE

# Eta squared
eta.MSPE = effectsize::eta_squared(fit.MSPE,ci = 0.95)
eta.MSPE

```

### Performance measures: MSPE

#### Data set


```{r}
Performance.MSPE.Mean = RM.Anova.MSPE
```


#### Mean and standard deviation

##### Across the number of time points

```{r}
kable(Performance.MSPE.Mean %>% 
  group_by(Model,Time) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.MSPE.Mean %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.MSE = mean(MSPE),
            sd.MSE = sd(MSPE)), digits = 3)
```

#### Boxplots


##### Across the number of time points

```{r}
Boxplot_MSPE_MAR_RE_Time = ggplot(Performance.MSPE.Mean, aes(x=as.factor(Time), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSPE",x="Number of time points")
Boxplot_MSPE_MAR_RE_Time

ggsave("Boxplot_MSPE_MAR_RE_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_MSPE_MAR_RE_Persons = ggplot(Performance.MSPE.Mean, aes(x=as.factor(Persons), y=MSPE, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() +
labs(y = "MSPE", x="Number of persons")
Boxplot_MSPE_MAR_RE_Persons

ggsave("Boxplot_MSPE_MAR_RE_Persons.png", width = 6, height = 4)

```


##### Method with the minimum MSE for each generated data set

```{r}
colMeans(table(Performance.MSPE.Mean %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE)])))
```

##### Method with the minimum MSE using the standard error rule for each generated data set

```{r}
colMeans(table(Performance.MSPE.Mean %>% 
  group_by(id.dat) %>% 
  summarize(min.MSE = Model[which.min(MSPE.1se)])))
```

