---
title: "Simulation results multilevel VAR(1) model with random effects"
authors: "Ginette Lafit"
date: 19-11-2020
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initial set up


```{r definition, echo = TRUE}
ls()

rm(list=ls())

library(ggplot2)
library(gridExtra)
library(sjstats)
library(dplyr)
library(knitr)
library(rstatix)

######################################################################################
######################################################################################
######################################################################################

# Upload the functions
source(file="Performance.VAR.Psi.AR.MSE.list.R")
source(file="Performance.VAR.Psi.CR.MSE.list.R")
source(file="Performance.VAR.Psi.AR.95CR.list.R")
source(file="Performance.VAR.Psi.CR.95CR.list.R")

######################################################################################
######################################################################################
######################################################################################

# Set the values to simulate data assuming a VAR(1) process
set.seed(123) # Set random seed
N = c(20,60,120) # Number of participants
T = c(50,100,200) # Number of time points
P = c(2,4,8) # Number of variables in VAR(1) models

Model.names = c('MAR.FE','MAR.RE','MVAR.FE','MVAR.RE','AR','VAR')

# Set the number of replicates
R = 100 # Number of replicates

```


### Repeated Measurement Anova

#### MSE for the autoregressive effects

```{r}
RM.Anova.MSE.Psi.AR = Performance.VAR.Psi.AR.MSE.list(N,T,P,R)
save(RM.Anova.MSE.Psi.AR, file = 'Results_Performance_MSE_Psi_AR_MVAR_RE.RData')

load(file = 'Results_Performance_MSE_Psi_AR_MVAR_RE.RData')

# Convert id and time into factor variables
RM.Anova.MSE.Psi.AR <- RM.Anova.MSE.Psi.AR %>%
  convert_as_factor(Time,Persons,Variables,Model,id)

RM.Anova.MSE.Psi.AR$id.dat = as.numeric(interaction(RM.Anova.MSE.Psi.AR$Time,RM.Anova.MSE.Psi.AR$Variables,
                                    RM.Anova.MSE.Psi.AR$Persons,RM.Anova.MSE.Psi.AR$id))

# MSE: Mixed ANOVA 

fit.MSE.Psi.AR = aov(
  MSE.Psi ~ Time*Persons*Variables*Model + Error(id.dat/Model),
  data = RM.Anova.MSE.Psi.AR
)

# Summary repeated measurement Anova
summary.anova.MSE.Psi.AR = summary(fit.MSE.Psi.AR)
summary.anova.MSE.Psi.AR

# Eta squared
eta.MSE.Psi.AR = effectsize::eta_squared(fit.MSE.Psi.AR,ci = 0.95)
eta.MSE.Psi.AR

```

#### MSE for the cross-regressive effects

```{r}
RM.Anova.MSE.Psi.CR = Performance.VAR.Psi.CR.MSE.list(N,T,P,R)
save(RM.Anova.MSE.Psi.CR, file = 'Results_Performance_MSE_Psi_CR_MVAR_RE.RData')

load(file = 'Results_Performance_MSE_Psi_CR_MVAR_RE.RData')

# Convert id and time into factor variables
RM.Anova.MSE.Psi.CR <- RM.Anova.MSE.Psi.CR %>%
  convert_as_factor(Time,Persons,Variables,Model,id)

RM.Anova.MSE.Psi.CR$id.dat = as.numeric(interaction(RM.Anova.MSE.Psi.CR$Time,RM.Anova.MSE.Psi.CR$Variables,
                                    RM.Anova.MSE.Psi.CR$Persons,RM.Anova.MSE.Psi.CR$id))

# MSE: Mixed ANOVA 

fit.MSE.Psi.CR = aov(
  MSE.Psi ~ Time*Persons*Variables*Model + Error(id.dat/Model),
  data = RM.Anova.MSE.Psi.CR
)

# Summary repeated measurement Anova
summary.anova.MSE.Psi.CR = summary(fit.MSE.Psi.CR)
summary.anova.MSE.Psi.CR

# Eta squared
eta.MSE.Psi.CR = effectsize::eta_squared(fit.MSE.Psi.CR,ci = 0.95)
eta.MSE.Psi.CR

```

#### 95% Coverage Rate for the autoregressive effect

```{r}
RM.Anova.95CR.Psi.AR = Performance.VAR.Psi.AR.95CR.list(N,T,P,R)
save(RM.Anova.95CR.Psi.AR, file = 'Results_Performance_95CR_Psi_AR_MVAR_RE.RData')

load(file = 'Results_Performance_95CR_Psi_AR_MVAR_RE.RData')

# Convert id and time into factor variables
RM.Anova.95CR.Psi.AR <- RM.Anova.95CR.Psi.AR %>%
  convert_as_factor(Time,Persons,Variables,Model,id)

RM.Anova.95CR.Psi.AR$id.dat = as.numeric(interaction(RM.Anova.95CR.Psi.AR$Time,RM.Anova.95CR.Psi.AR$Variables,
                                    RM.Anova.95CR.Psi.AR$Persons,RM.Anova.95CR.Psi.AR$id))

# 95% CR: Mixed ANOVA 

fit.95CR.Psi.AR = aov(
  CR.Psi ~ Time*Persons*Variables*Model + Error(id.dat/Model),
  data = RM.Anova.95CR.Psi.AR
)

# Summary repeated measurement Anova
summary.anova.95CR.Psi.AR = summary(fit.95CR.Psi.AR)
summary.anova.95CR.Psi.AR

# Eta squared
eta.MSE.95CR.AR = effectsize::eta_squared(fit.95CR.Psi.AR,ci = 0.95)
eta.MSE.95CR.AR
```


#### 95% Coverage Rate for the cross-regressive effect

```{r}
RM.Anova.95CR.Psi.CR = Performance.VAR.Psi.CR.95CR.list(N,T,P,R)
save(RM.Anova.95CR.Psi.CR, file = 'Results_Performance_95CR_Psi_CR_MVAR_RE.RData')

load(file = 'Results_Performance_95CR_Psi_CR_MVAR_RE.RData')

# Convert id and time into factor variables
RM.Anova.95CR.Psi.AR <- RM.Anova.95CR.Psi.AR %>%
  convert_as_factor(Time,Persons,Variables,Model,id)

RM.Anova.95CR.Psi.AR$id.dat = as.numeric(interaction(RM.Anova.95CR.Psi.AR$Time,RM.Anova.95CR.Psi.AR$Variables,
                                    RM.Anova.95CR.Psi.AR$Persons,RM.Anova.95CR.Psi.AR$id))

# 95% CR: Mixed ANOVA 

fit.95CR.Psi.AR = aov(
  CR.Psi ~ Time*Persons*Variables*Model + Error(id.dat/Model),
  data = RM.Anova.95CR.Psi.AR
)

# Summary repeated measurement Anova
summary.anova.95CR.Psi.AR = summary(fit.95CR.Psi.AR)
summary.anova.95CR.Psi.AR

# Eta squared
eta.MSE.95CR.AR = effectsize::eta_squared(fit.95CR.Psi.AR,ci = 0.95)
eta.MSE.95CR.AR
```

#### Performance measure: MSE for the autoregressive effects 

```{r}
Performance.MSE.AR.Mean = RM.Anova.MSE.Psi.AR

```

#### Mean and standard deviation

##### Across the number of variables

```{r}
kable(Performance.MSE.AR.Mean %>% 
  group_by(Model,Variables) %>% 
  summarize(mean.MSE = mean(MSE.Psi),
            sd.MSE = sd(MSE.Psi)), digits = 3)
```


##### Across the number of time points

```{r}
kable(Performance.MSE.AR.Mean %>% 
  group_by(Model,Time) %>% 
  summarize(mean.MSE = mean(MSE.Psi),
            sd.MSE = sd(MSE.Psi)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.MSE.AR.Mean %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.MSE = mean(MSE.Psi),
            sd.MSE = sd(MSE.Psi)), digits = 3)
```

#### Boxplots

##### Across the number of variables

```{r}
Boxplot_MSE_Psi_AR_MVAR_RE_Variables = ggplot(Performance.MSE.AR.Mean, aes(x=as.factor(Variables), y=MSE.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSE autoregressive effects", x="Number of Variables")
Boxplot_MSE_Psi_AR_MVAR_RE_Variables

ggsave("Boxplot_MSE_Psi_AR_MVAR_RE_Variables.png", width = 6, height = 4)

```

##### Across the number of time points

```{r}
Boxplot_MSE_Psi_AR_MVAR_RE_Time = ggplot(Performance.MSE.AR.Mean, aes(x=as.factor(Time), y=MSE.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSE autoregressive effects", x="Number of time points")
Boxplot_MSE_Psi_AR_MVAR_RE_Time

ggsave("Boxplot_MSE_Psi_AR_MVAR_RE_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_MSE_Psi_AR_MVAR_RE_Persons = ggplot(Performance.MSE.AR.Mean, aes(x=as.factor(Persons), y=MSE.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSE autoregressive effects", x="Number of persons")
Boxplot_MSE_Psi_AR_MVAR_RE_Persons

ggsave("Boxplot_MSE_Psi_AR_MVAR_RE_Persons.png", width = 6, height = 4)

```

#### Performance measure: MSE for the cross-regressive effects 

```{r}
Performance.MSE.CR.Mean = RM.Anova.MSE.Psi.CR

```

#### Mean and standard deviation

##### Across the number of Variables

```{r}
kable(Performance.MSE.CR.Mean %>% 
  group_by(Model,Variables) %>% 
  summarize(mean.MSE = mean(MSE.Psi),
            sd.MSE = sd(MSE.Psi)), digits = 3)
```


##### Across the number of time points

```{r}
kable(Performance.MSE.CR.Mean %>% 
  group_by(Model,Time) %>% 
  summarize(mean.MSE = mean(MSE.Psi),
            sd.MSE = sd(MSE.Psi)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.MSE.CR.Mean %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.MSE = mean(MSE.Psi),
            sd.MSE = sd(MSE.Psi)), digits = 3)
```

#### Boxplots

##### Across the number of variables

```{r}
Boxplot_MSE_Psi_CR_MVAR_RE_Variables = ggplot(Performance.MSE.CR.Mean, aes(x=as.factor(Variables), y=MSE.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSE cross-regressive effects", x="Number of variables")
Boxplot_MSE_Psi_CR_MVAR_RE_Variables

ggsave("Boxplot_MSE_Psi_CR_MVAR_RE_Variables.png", width = 6, height = 4)

```

##### Across the number of time points

```{r}
Boxplot_MSE_Psi_CR_MVAR_RE_Time = ggplot(Performance.MSE.CR.Mean, aes(x=as.factor(Time), y=MSE.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSE cross-regressive effects", x="Number of time points")
Boxplot_MSE_Psi_CR_MVAR_RE_Time

ggsave("Boxplot_MSE_Psi_CR_MVAR_RE_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_MSE_Psi_CR_MVAR_RE_Persons = ggplot(Performance.MSE.CR.Mean, aes(x=as.factor(Persons), y=MSE.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "MSE cross-regressive effects", x="Number of persons")
Boxplot_MSE_Psi_CR_MVAR_RE_Persons

ggsave("Boxplot_MSE_Psi_CR_MVAR_RE_Persons.png", width = 6, height = 4)

```


#### Performance measure: 95% CR for the autoregressive effects 

```{r}
Performance.95CR.AR.Mean = RM.Anova.95CR.Psi.AR

```

#### Mean and standard deviation

##### Across the number of variables

```{r}
kable(Performance.95CR.AR.Mean %>% 
  group_by(Model,Variables) %>% 
  summarize(mean.CR = mean(CR.Psi),
            sd.CR = sd(CR.Psi)), digits = 3)
```

##### Across the number of time points

```{r}
kable(Performance.95CR.AR.Mean %>% 
  group_by(Model,Time) %>% 
  summarize(mean.CR = mean(CR.Psi),
            sd.CR = sd(CR.Psi)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.95CR.AR.Mean %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.CR = mean(CR.Psi),
            sd.CR = sd(CR.Psi)), digits = 3)
```

#### Boxplots

##### Across the number of variables

```{r}
Boxplot_95CR_Psi_AR_MVAR_RE_Variables = ggplot(Performance.95CR.AR.Mean, aes(x=as.factor(Variables), y=CR.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "95% Coverage rate autoregressive effects", x="Number of variables")
Boxplot_95CR_Psi_AR_MVAR_RE_Variables

ggsave("Boxplot_95CR_Psi_AR_MVAR_RE_Variables.png", width = 6, height = 4)

```


##### Across the number of time points

```{r}
Boxplot_95CR_Psi_AR_MVAR_RE_Time = ggplot(Performance.95CR.AR.Mean, aes(x=as.factor(Time), y=CR.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "95% Coverage rate autoregressive effects", x="Number of time points")
Boxplot_95CR_Psi_AR_MVAR_RE_Time

ggsave("Boxplot_95CR_Psi_AR_MVAR_RE_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_95CR_Psi_AR_MVAR_RE_Persons = ggplot(Performance.95CR.AR.Mean, aes(x=as.factor(Persons), y=CR.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "95% Coverage rate autoregressive effects", x="Number of persons")
Boxplot_95CR_Psi_AR_MVAR_RE_Persons

ggsave("Boxplot_95CR_Psi_AR_MVAR_RE_Persons.png", width = 6, height = 4)

```


#### Performance measure: 95% CR for the cross-regressive effects 

```{r}
Performance.95CR.CR.Mean = RM.Anova.95CR.Psi.CR

```

#### Mean and standard deviation

##### Across the number of variables

```{r}
kable(Performance.95CR.CR.Mean %>% 
  group_by(Model,Variables) %>% 
  summarize(mean.CR = mean(CR.Psi),
            sd.CR = sd(CR.Psi)), digits = 3)
```

##### Across the number of time points

```{r}
kable(Performance.95CR.CR.Mean %>% 
  group_by(Model,Time) %>% 
  summarize(mean.CR = mean(CR.Psi),
            sd.CR = sd(CR.Psi)), digits = 3)
```

##### Across the number of persons

```{r}
kable(Performance.95CR.CR.Mean %>% 
  group_by(Model,Persons) %>% 
  summarize(mean.CR = mean(CR.Psi),
            sd.CR = sd(CR.Psi)), digits = 3)
```

#### Boxplots

##### Across the number of variables

```{r}
Boxplot_95CR_Psi_CR_MVAR_RE_Variables = ggplot(Performance.95CR.CR.Mean, aes(x=as.factor(Variables), y=CR.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "95% Coverage rate cross-regressive effects", x="Number of variables")
Boxplot_95CR_Psi_CR_MVAR_RE_Variables

ggsave("Boxplot_95CR_Psi_CR_MVAR_RE_Variables.png", width = 6, height = 4)

```


##### Across the number of time points

```{r}
Boxplot_95CR_Psi_CR_MVAR_RE_Time = ggplot(Performance.95CR.CR.Mean, aes(x=as.factor(Time), y=CR.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "95% Coverage rate cross-regressive effects", x="Number of time points")
Boxplot_95CR_Psi_CR_MVAR_RE_Time

ggsave("Boxplot_95CR_Psi_CR_MVAR_RE_Time.png", width = 6, height = 4)

```

##### Across the number of persons

```{r}
Boxplot_95CR_Psi_CR_MVAR_RE_Persons = ggplot(Performance.95CR.CR.Mean, aes(x=as.factor(Persons), y=CR.Psi, fill = Model)) + 
  geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=4, size=1) + facet_wrap(~Model) + scale_fill_grey() + theme_bw() + 
labs(y = "95% Coverage rate cross-regressive effects", x="Number of persons")
Boxplot_95CR_Psi_CR_MVAR_RE_Persons

ggsave("Boxplot_95CR_Psi_CR_MVAR_RE_Persons.png", width = 6, height = 4)

```